Verifying Spatial Properties of Array Computations

### 2017-04-15 oopsla17/oopsla17.tex
Fix denotational semantics intro

\noindent
An interpretation function $\interp{-}_N$ maps closed\footnote{That
  is, we assume there are no occurrences of \textit{rvar} in a
  specification being modelled.  Any \emph{open} specification
  containing region variables can be made closed by straightforward
  syntactic substitution with a (closed) \textit{region}.}
specifications to sets of $N$-dimensional index schemes with modifier
information, \ie{} specifications are mapped to
$\textsf{Mult} (\textsf{Approx} (\mathcal{P}({\bz})^N))$ where $N$ is
the maximum dimensionality of the specification being modelled.

>>>>

\noindent
An interpretation function $\interp{-}_N$ maps closed\footnote{That
  is, we assume there are no occurrences of \textit{rvar} in a
  specification being modelled.  Any \emph{open} specification
  containing region variables can be made closed by straightforward
  syntactic substitution with a (closed) \textit{region}.}
specifications to sets of $N$-dimensional index schemes with modifier
information, \ie{} specifications are mapped to
$\textsf{Mult} (\textsf{Approx} (\region{N}))$.
